---
title: "Intro to the App"
#author: "Soumadip Roy"
#date: "March 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


iris is a famous dataset for those who start working on R. We have the following fields in the dataset

```{r iris , warning=FALSE, message = FALSE, echo=FALSE}
names(iris)
```

The dataset has data for sepal and petal attributes for the 3 species 

```{r warning=FALSE, message = FALSE, echo=FALSE}
unique(iris$Species)
```

In this shiny app we would try to study the various combinations of the attributes and how they related to each other.
We have 4 options of the for the graphs

- Petal.Length ~ Sepal.Length
- Petal.Width ~ Sepal.Width
- Petal.Width ~ Petal.Length
- Sepal.Width ~ Sepal.Length

As an user of this app, select the graph options and the corresponding graph would come up.

You also have the option to look into the full dataset and statistical summary of the dataset in the other 2 tables available.